---
title: "Strength << >> OA Leave-one-out Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(broom)
library(meta)
library(metafor)

quadsoa_cleaned <- read.csv("data/processed/Strength OA Review Cleaned.csv")

# Takagi paper presents two populations  - with OA and at risk of OA. These subgroups will be used in a later sensitivity analysis. 
# For now need to combine together for the main analysis - using a 'pre-meta-analysis
takagi <- quadsoa_cleaned %>%
  filter(author == "Takagi") %>% 
  group_by(author, sex, analysis_group) %>% # group by each publication and subgroups of interest in this review, for later 'pre-metaanalyses'
  nest(data = -c(studyname:year, outcome:muscle_test, reference_group, explanatory_group)) %>%# nest data, remove data that is consistent across subgroups
  mutate(rma = map(data, ~tidy(rma(yi, vi, data = .x)) %>% # for each group, perform a rma
                     select(estimate, std.error) %>% # take only the estimated log rr and log se
                     rename(yi = estimate, # rename for consistency with final dataframe
                            sei = std.error) %>%
                     mutate(vi = sei^2)
  )) %>%
  select(-data) %>% # remove the original data as no longer needed
  unnest(cols = c(rma)) # un-nest back to same format

# now need to join the 'pre-meta' data back to the original dataset
quadsoa_analysis <- quadsoa_cleaned %>% 
  filter(author != "Takagi") %>% # take all data not split before
  bind_rows(., takagi) # bind the pre-meta data 

# Order and arrange
quadsoa_analysis <- quadsoa_analysis %>%
  mutate(sex = factor(sex, levels = c("mixed", "Men", "Women", "Overall"))) %>%
  arrange(outcome, analysis_group, muscle, sex) # order and arrange data frame

### For Primary Analyses

primary_meta_loo <- quadsoa_analysis %>%
  filter(analysis_group %in% c("medial tf", "whole tf", "lateral pf", "whole pf") &
           studyname != "Culvenor 2019" & # Exclude Culvenor as overlaps with Segal 2010
           !(studyname == "Dannhauer 2014" & muscle == "quad")) %>% # Dannhauer and Culvenor removed due to data duplication
  mutate(analysis_group = case_when(
    str_detect(analysis_group, "tf") ~ "tf",
    str_detect(analysis_group, "pf") ~ "pf"
  )) %>%
  group_by(analysis_group, muscle) %>% # group by each publication and subgroups of interest in this review, for later 'pre-meta-analyses'
  mutate(k = length(studyname)) %>%
  nest(data = -c(analysis_group:muscle, k)) %>%# nest data, remove data that is consistent across subgroups
  ungroup() %>%
  mutate(rma = map(data, ~rma(yi, vi, data = .x)), # runs metafor meta-analysis
         metaforinf = map_if(rma,  # ruin a influence analysis from metafor package if k>1
                             k > 1, 
                             ~influence(.x) %>% pluck(1) %>% data.frame, # take the output
                             .else = ~data.frame(inf = NA))) %>% # for k <=1 return df with NAs
  mutate(new = map2(data, metaforinf, ~bind_cols(.x, .y))) %>% # combine influence data with original data
  mutate(new = map(new, ~.x %>%
                     mutate(studyname = case_when(
                       sex != "mixed" ~ paste(studyname, sex),
                       TRUE ~ studyname)))) %>%
  select(-c(data, rma, metaforinf)) %>% # remove all nested columns now not needed
  # now run meta with metagen (inorder to get nice influence plots)
  mutate(rma = map(new, ~metagen(TE = yi, seTE = sei, studlab = studyname, data = .x, sm = "RR")),
         influence = map_if(rma, k > 1, ~metainf(.x, pooled = "random"))) # run influence analysis with meta package

  
           

### For Secondary Analyses
secondary_meta_loo <- quadsoa_analysis %>%
  group_by(outcome, analysis_group, muscle) %>% # group by each publication and subgroups of interest in this review, for later 'pre-meta-analyses'
  mutate(k = length(studyname)) %>%
  nest(data = -c(outcome, analysis_group:muscle, k)) %>%# nest data, remove data that is consistent across subgroups
  ungroup() %>%
  mutate(rma = map(data, ~rma(yi, vi, data = .x)), # runs metafor meta-analysis
         metaforinf = map_if(rma,  # ruin a influence analysis from metafor package if k>1
                             k > 1, 
                             ~influence(.x) %>% pluck(1) %>% data.frame, # take the output
                             .else = ~data.frame(inf = NA))) %>% # for k <=1 return df with NAs
  mutate(new = map2(data, metaforinf, ~bind_cols(.x, .y))) %>% # combine influence data with original data
  mutate(new = map(new, ~.x %>%
                     mutate(studyname = case_when(
                       sex != "mixed" ~ paste(studyname, sex),
                       TRUE ~ studyname)))) %>%
  select(-c(data, rma, metaforinf)) %>% # remove all nested columns now not needed
  # now run meta with metagen (inorder to get nice influence plots)
  mutate(rma = map(new, ~metagen(TE = yi, seTE = sei, studlab = studyname, data = .x, sm = "RR")),
         influence = map_if(rma, k > 1, ~metainf(.x, pooled = "random"))) # run influence analysis with meta package
  
```

#### Sensitivity Leave-One-Out Analyses for all meta-analyses completed
These are only for overall combined (i.e no sex subgroup), and analyses with over 2 observations

"Sig Influence" in each plot refers to whether a study has statistical influence (based on cut-offs from various model parameters, and doesn't necessarily correspond to the overall effect estimate changing. A simpler way to look at this is does the overall estimate change

# Primary Analyses

## 1.1 Tibiofemoral - Quads

```{r tf quad, echo = FALSE, fig.width = 8}
pluck(primary_meta_loo$influence) %>% pluck(2) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

## 1.2 Tibiofemoral - Hamstring

```{r tf hs, echo = FALSE, fig.width = 8}
pluck(primary_meta_loo$influence) %>% pluck(1) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

## 1.3 Patellofemoral - Quads

```{r pf quad, echo = FALSE, fig.width = 8}
pluck(primary_meta_loo$influence) %>% pluck(3) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 3))
```

# Secondary Analyses

## 1 Radiographic Worsening

### 1.1 Radiographic Worsening - Quad Strength - Whole TF

```{r radiogrphic quad, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(12) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

### 1.2 Radiographic Worsening - Quad Strength - Whole PF
```{r radiogrphic quadpf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(10) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.33, 3))
```

### 1.3 Radiographic Worsening - Hamstring Strength - Whole TF
```{r radiogrphic hstf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(11) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

## 2 Joint Space Narrowing

### 2.1 Joint Space Narrowing - Quad Strength - Medial TF
```{r jsn quad, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(4) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

## 3 Cartilage Thinning

### 3.1 Cartilage Thinning - Quad Strength - Medial TF
```{r thinning quad, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(2) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.33, 3))
```

## 4 Cartilage Lesion Worsening

### 4.1 Cartilage Lesion Worsening - Quad Strength - Medial TF
```{r semi quadmedtf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(8) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

### 4.2 Cartilage Lesion Worsening - Quad Strength - Lateral TF
```{r semi quadlattf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(6) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

### 4.3 Cartilage Lesion Worsening - Quad Strength - Medial PF
```{r semi quadmedpf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(7) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

### 4.4 Cartilage Lesion Worsening - Quad Strength - Lateral PF
```{r semi quadlatpf, echo = FALSE, fig.width = 8}
pluck(secondary_meta_loo$influence) %>% pluck(5) %>%
forest.meta(., 
            lower.equi = exp(last(.$lower)), 
            upper.equi = exp(last(.$upper)), 
            col.equi = "green", 
            fill.equi = "green",
            leftcols = c("studlab", "inf"),
            leftlabs = c("Analysis", "Sig Influence"),
            text.random = "Original random effects model\n(All studies included)",
            rightcols = c("effect.ci", "I2"),
            backtransf = TRUE,
            fontfamily = "Karla",
            xlim = c(0.5, 2))
```

